A Bidirected String Graph Model of Genome Assembly

### 2012-11-29 presentation/presentation.tex
presentation

\usepackage{graphicx}
\usepackage{listings}
\usepackage{comment}
\usepackage{float}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{multicol}

@@

>>>>

\usepackage{graphicx}
\usepackage{listings}
\usepackage{comment}
\usepackage{float}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{multicol}
\usepackage{grffile}

@@

%make -B SAMPLE_SIZE=450 out.reduced.mapped.bidigraph.pdf out.reduced.mapped.collapsed.bidigraph.pdf out.bidigraph.pdf GENOME=rep.fa COVERAGE=5

\begin{frame}{Another example}
	\begin{figure}[H]
		\includegraphics[scale=0.25]{example.bidigraph-crop.pdf}	
		\caption{Bidirected string graph built from 100 bp reads sampled
		randomly at 5 $\times$ coverage from a 450 bp genome, using minimum 25
		bp overlaps.  Note: edges are labeled with their lengths, not DNA
		sequences.}
	\end{figure}
\end{frame}

\begin{frame}{Another example (cont.)}
	\begin{figure}[H]
		\includegraphics[scale=0.7]{example.reduced.mapped.bidigraph-crop.pdf}	
		\caption{The bidirected string graph from the previous slide, after
		transitive reduction.}
	\end{figure}
\end{frame}

\begin{frame}{Another example (cont.)}
	\begin{figure}[H]
		\includegraphics[scale=0.7]{example.reduced.mapped.collapsed.bidigraph-crop.pdf}	
		\caption{The bidirected string graph from the previous slide, after
		collapsing unbranched paths.}
	\end{figure}
\end{frame}
